Initial Analysis

### 2019-08-21 Initial_Analysis.Rmd
Made some ch-ch-ch-changes to script

# Set paths depending on machine Beast (jepa88), "carmelia" or Hall1000
if(Sys.info()[7] == "jepa88"){
  Data_Path <- "Z:/JULIANO_NEYMAR/FishForVisa/"
  Path <- paste(Data_Path,"Results/All_Models/",sep = "")
  }
if(Sys.info()[7] == "carmelia"){
  Data_Path <- "~/GitHub/FishForVisa/Temporal_Data/"
  Path <- paste(Data_Path,sep = "")
}else{
  Data_Path <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/"
  Path <- paste(Data_Path,"Results/",sep = "")
}

@@

```{r Speceis_Models, eval = F, echo = T}

@@

@@

Mclapply_Hack <- function(...){
    ## Create a cluster
    size.of.list <- length(list(...)[[1]])
    cl <- makeCluster(min(size.of.list, detectCores()))

@@

# Set Spceies list
Exploited_Species <- fread(paste(Data_Path,"Distribution_Data/exploited_species_list.csv",sep="")) %>%
  filter(TaxonKey %in% Species_List)

@@

@@

system.time(
  Spp_Trans <- bind_rows(
    mclapply(
      Exploited_Species_List, FUN =EstTransIndex, Model = "All", Neighbors = Neighbor_List,Coord = CoorG
    )
  )
)

   # user  system elapsed (For three spp in Hall1000)
 # 13.430   5.126  35.059 
### Save Test

# write.csv(Spp_Trans,
#           "central_america_trans.csv",
#           row.names = F)
# 
```

@@

```{r Load_Data, eval = F}

# Transboundary data
Spp <- list.files(Results_Path)
Results_Data <- GetTransResults(Spp)

# Data needed to remove duplicates
sau_eez_fes <- read.csv(paste(Data_Path,"Spatial_Data/sau_eez_fes.csv",sep=""))

@@

# head(Results_Data)
# unique(Results_Data$Model_Index)
length(unique(Results_Data$TaxonKey)) #672 spp

# Clean_Results <- Results_Data

@@

@@

```{Number_Tran_country, eval =F, echo =F}

Clean_Results <- Indexes %>%   
  rename(FishingRegion=Country_Territory) %>% 
  left_join(Clean_sau_eez_fes,
            by = "FishingRegion") %>% 
  select(Model,
         TaxonKey,
         Country_Territory= FishingRegion,
         FishingRegion=Neighbor_Territory,
         Area_Index,
         CT_fishing_entity= fishing_entity) %>% 
  left_join(Clean_sau_eez_fes,
            by = "FishingRegion") %>% 
  select(#1,2, 
         Neighbor_Territory = FishingRegion,
         #Model_Index:CT_fishing_entity,
         NT_fishing_entity= fishing_entity,
         everything()
  ) %>% 
  mutate(
    CT_fishing_entity = ifelse(is.na(CT_fishing_entity),paste(Country_Territory),paste(CT_fishing_entity)),
    NT_fishing_entity = ifelse(is.na(NT_fishing_entity),paste(Neighbor_Territory),paste(NT_fishing_entity)),
    Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
  )

# Manually deal with NAs... Ughhhhh
Results_NA <- Clean_Results %>% 
  filter(is.na(Same_Nation)) %>% 
  group_by(Country_Territory,Neighbor_Territory) %>% 
  summarise(n())

# TI of 10% and MI > 50

>>>>

# Set paths depending on machine Beast (jepa88), "carmelia" or Hall1000
if(Sys.info()[7] == "jepa88"){
  Data_Path <- "Z:/JULIANO_NEYMAR/FishForVisa/"
  Path <- paste(Data_Path,"Results/All_Models/",sep = "")
  }
if(Sys.info()[7] == "carmelia"){
  Data_Path <- "~/GitHub/FishForVisa/Temporal_Data/"
  Path <- paste(Data_Path,sep = "")
}
if(Sys.info()[7] == "hall1000"){
  Data_Path <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/"
  Path <- paste(Data_Path,"Results/",sep = "")
}

@@

```{r Speceis_List_For_Data, eval = F, echo = T}

@@

# Get All SAU species for the final analysis

@@

Mclapply_Hack <- function(...){
    ## Create a cluster
    size.of.list <- length(list(...)[[1]])

    cl <- makeCluster(min(size.of.list, n_cores))

@@

# Set Spceies list
Exploited_Species <- fread(paste(Data_Path,"Distribution_Data/exploited_species_list.csv",sep="")) %>%
  filter(!TaxonKey %in% Species_List)

@@

# NUmber of cores to us 
# n_cores <- detectCores()

@@

system.time(
  Spp_Trans <- bind_rows(
    mclapply(
      Exploited_Species_List, FUN =EstTransIndex, Model = "All", Neighbors = Neighbor_List, Coord = CoorG
    )
  )
)

@@

```{r Load_Results_Data, eval = F}

# Spatial Data needed to remove duplicates
sau_eez_fes <- read.csv(paste(Data_Path,"Spatial_Data/sau_eez_fes.csv",sep=""))

@@

# Transboundary Results
Spp <- list.files(Results_Path)[1:675]

Results_Trans <- GetTransResults(Spp)

Clean_Results_Trans <- Results_Trans %>%   
  rename(FishingRegion=Country_Territory) %>% 
  left_join(Clean_sau_eez_fes,
            by = "FishingRegion") %>% 
  select(Model,
         TaxonKey,
         Country_Territory= FishingRegion,
         FishingRegion=Neighbor_Territory,
         Area_Index,
         CT_fishing_entity= fishing_entity) %>% 
  left_join(Clean_sau_eez_fes,
            by = "FishingRegion") %>% 
  select(#1,2, 
    Neighbor_Territory = FishingRegion,
    #Model_Index:CT_fishing_entity,
    NT_fishing_entity= fishing_entity,
    everything()
  ) %>% 
  mutate(
    CT_fishing_entity = ifelse(is.na(CT_fishing_entity),paste(Country_Territory),paste(CT_fishing_entity)),
    NT_fishing_entity = ifelse(is.na(NT_fishing_entity),paste(Neighbor_Territory),paste(NT_fishing_entity)),
    Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
  )

# Load results for non transboundary (discrete) stocks
Results_Discrete <- fread(paste(Results_Path,"Non_Transboundary_Data.csv",sep=""))

@@

```{r Results_Tresholds, eval =F, echo = F}

@@

```{Tran_country, eval =F, echo =F}

# Number of Transboundary Species
length(unique(Results_Trans$TaxonKey)) #675 spp

# Number of Discret EEZ species
length(unique(Results_Discrete$TaxonKey))

```{Tran_country_Map, eval =F, echo =F}
